D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-04 ootavacuous.tex
"Illustrative Litmus Tests": Remove bogus conjectures
There really are cases where locating an OOTA cycle would require
looking at more than one branch of a complex semantic dependency.
Therefore, remove counterfactual conjectures.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
"Illustrative Litmus Tests": Add section references
The work suggested in the "Non-Trivial Semantic Dependencies" appendix
has been done, so add references to the corresponding sections.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Note that in a C++ implementation that (erroneously) permitted an OOTA
cycle to form, that cycle would involve both \co{r0} and \co{r1}.
However, we conjecture that tools designed to find OOTA cycles could
satisfy themselves with having found either of the two resulting cycles.

@@

In both
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero},
an OOTA cycle (such as the one indicated by their \co{exists} clauses)
would need to affect both the \co{x} and the \co{y} components of this
compound semantic dependency.
However, we again conjecture that tools designed to find OOTA cycles could
satisfy themselves with having found either of the two resulting cycles.
This situation poses a challenge to current work on semantic dependencies,
which typically restricts such dependencies to a single load and store.

@@

This raises the question of how to determine the set of semantic
dependencies in a given execution of a given fragment of code.
The short answer is that when running on a real-world system, 
any C++ program is a finite-state machine, which, unlike Turing-complete
systems, can be analyzed.
% @@@ reference to cbmc appendix.

@@

This situation further underscores the per-execution nature of semantic
dependencies as well as the need for an improved definition of ``semantic
dependency''.
We propose expanding the traditional definition to include dependencies
extending from groups of loads to a single store.

>>>>

Note that in a C++ implementation that (erroneously) permitted an OOTA
cycle to form, that cycle would involve both \co{r0} and \co{r1}.

@@

In both
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero},
an OOTA cycle (such as the one indicated by their \co{exists} clauses)
would need to affect both the \co{x} and the \co{y} components of this
compound semantic dependency.
This situation poses a challenge to current work on semantic dependencies,
which typically restricts such dependencies to a single load and store.

@@

This raises the question of how to determine the set of semantic
dependencies in a given execution of a given fragment of code.
The short answer is that when running on a real-world system, 
any C++ program is a finite-state machine, which, unlike Turing-complete
systems, can be analyzed, as demonstrated in
Section~\ref{sec:Hardware Dependencies, Instruction Ordering, and the Fundamental Property}.

@@

This situation further underscores the per-execution nature of semantic
dependencies as well as the need for an improved definition of ``semantic
dependency''.
In
Section~\ref{sec:A Definition of Semantic Dependency},
we expand the traditional definition to include dependencies extending
from groups of loads to a single store.
